% ── 中文摘要 ──
\renewcommand{\abstractname}{摘\quad 要}
\begin{abstract}
个性化城市路径规划需要协调美食探索、观光游览、休闲漫步、特种兵打卡等异构用户偏好与时空预算约束。现有方法要么依赖无法理解自然语言意图的经典优化求解器，要么使用单LLM管线，产生空间不一致的路线和虚假POI。本文提出\textbf{CityFlow}，一种专家集成多智能体框架，通过11个领域专家的分工协作，由LangGraph状态机编排完成路径规划。受混合专家条件计算思想启发，CityFlow的核心机制包括：（1）场景感知的专家分派，将用户意图分类为5种场景类型并动态激活相关专家；（2）基于两波次依赖排序的并行专家执行；（3）评审-返工反馈环，从6个质量维度评估方案并进行算法级空间验证；（4）算法级时间平滑，对LLM生成的时间分配进行验证与修正。在覆盖珠海（2000+POI）的100个多样化场景上，CityFlow通过率为90\%，平均得分74.3/100（等级分布：S:12, A:24, B:23, C:30, D:10, F:1）。多模型对比实验表明，廉价小模型（讯飞xopqwen35v35b，约\$0.15/M tokens）在专家集成架构下优于昂贵的前沿模型（DeepSeek Chat，约\$1/M tokens），成本降低约6倍。消融分析和7轮系统优化记录表明，专家分解、场景感知分派和时间平滑是性能提升的关键因素。

\textbf{关键词}：多智能体系统；大语言模型；路径规划；专家集成；混合专家
\end{abstract}

% ── English Abstract ──
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
Personalized urban route planning requires reconciling heterogeneous user preferences---culinary exploration, scenic sightseeing, leisure pacing, or speed-run touring---with spatial, temporal, and budgetary constraints. Existing approaches either rely on classical optimization solvers that cannot interpret natural language intent, or single-LLM pipelines that hallucinate POIs and produce spatially incoherent routes. We present \textbf{CityFlow}, an expert-ensemble multi-agent framework that decomposes route planning across 11 domain-specific experts orchestrated by a LangGraph state machine. Inspired by the Mixture-of-Experts principle of conditional computation through specialized modules, CityFlow features: (1)~scene-aware expert dispatch that classifies user intent into five scenario types and dynamically activates only relevant experts; (2)~parallel wave-based expert execution across two dependency-ordered waves; (3)~a review-rework feedback loop evaluating proposals against six quality dimensions with algorithmic spatial verification; and (4)~algorithmic time smoothing that validates and corrects LLM-generated temporal allocations. Evaluated on 100 diverse scenarios covering Zhuhai (2000+ POIs), CityFlow achieves 90\% pass rate with an average score of 74.3/100 (grade distribution: S:12, A:24, B:23, C:30, D:10, F:1). On 5 core scenarios, the LLM-judge average is 7.4/10 with 5/5 pass rate. A multi-model A/B test reveals that inexpensive small models (qwen3.5-flash, \$0.2/M tokens) outperform expensive frontier models (DeepSeek Chat, \$1/M tokens) when embedded in the expert-ensemble architecture, with the iFlytek xopqwen35v35b model achieving the best score at approximately 6$\times$ lower cost. An analysis of optimization history demonstrates that expert-ensemble decomposition outperforms rule-based alternatives by 1.0 point (6.4 vs.\ 7.4, commit \texttt{d323625}), with the largest improvements from algorithmic time smoothing (+3.0 points on speed-run scenarios, commit \texttt{487f99a}).

\textbf{Keywords}: multi-agent system; large language model; route planning; expert ensemble; mixture of experts
\end{abstract}
