\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{ctex}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
% natbib removed: using inline thebibliography
\usepackage{float}
\usepackage{caption,subcaption}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,fit,backgrounds}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    citecolor=black,
    urlcolor=black
}

\definecolor{accent}{HTML}{4FACFE}
\definecolor{coral}{HTML}{FF6B6B}
\definecolor{forest}{HTML}{51CF66}

\title{\textbf{CityFlow}: Expert-Ensemble Multi-Agent Collaboration\\for Personalized Urban Route Planning}

\author{%
  王其龙\textsuperscript{1}\\[2pt]
  \textsuperscript{1}北京师范大学 珠海校区\\[2pt]
  \texttt{13623753581@163.com}%
}

\begin{document}

\maketitle

\input{sections/abstract}

\input{sections/introduction}

\input{sections/related_work}

\input{sections/method}

\input{sections/experiments}

\input{sections/discussion}

\input{sections/conclusion}

% ── References (embedded, tectonic doesn't run bibtex) ──
\begin{thebibliography}{30}

\bibitem{toth2014vehicle}
Toth, P. and Vigo, D. (2014).
\newblock Vehicle Routing: Problems, Methods, and Applications.
\newblock SIAM.

\bibitem{solomon1987algorithms}
Solomon, M.~M. (1987).
\newblock Algorithms for the vehicle routing and scheduling problems with time window constraints.
\newblock \emph{Operations Research}, 35(2):254--265.

\bibitem{wei2022chain}
Wei, J., Wang, X., Schuurmans, D., et~al. (2022).
\newblock Chain-of-thought prompting elicits reasoning in large language models.
\newblock \emph{NeurIPS}, 35:24824--24837.

\bibitem{ji2023survey}
Ji, Z., Lee, N., Frieske, R., et~al. (2023).
\newblock Survey of hallucination in natural language generation.
\newblock \emph{ACM Computing Surveys}, 55(12):1--38.

\bibitem{gu2024llmjudge}
Gu, J., Jiang, X., Shi, Z., et~al. (2024).
\newblock A survey on LLM-as-a-Judge.
\newblock \emph{arXiv:2411.15594}.

\bibitem{shazeer2017outrageously}
Shazeer, N., Mirhoseini, A., et~al. (2017).
\newblock Outrageously large neural networks: The sparsely-gated mixture-of-experts layer.
\newblock \emph{ICLR}.

\bibitem{jiang2024mixtral}
Jiang, A.~Q., Sablayrolles, A., et~al. (2024).
\newblock Mixtral of experts.
\newblock \emph{arXiv:2401.04088}.

\bibitem{fedus2022switch}
Fedus, W., Zoph, B., and Shazeer, N. (2022).
\newblock Switch transformers: Scaling to trillion parameter models with simple and efficient sparsity.
\newblock \emph{JMLR}, 23(120):1--39.

\bibitem{chen2024travelagent}
Chen, A., Ge, X., Fu, Z., Xiao, Y., and Chen, J. (2024).
\newblock TravelAgent: An AI assistant for personalized travel planning.
\newblock \emph{arXiv:2409.08069}.

\bibitem{han2024travelplanner}
Han, J., Xie, H., Zhu, F., et~al. (2024).
\newblock TravelPlanner: A benchmark for real-world planning with language agents.
\newblock \emph{arXiv:2402.01622}.

\bibitem{wu2023autogen}
Wu, Q., Bansal, G., et~al. (2023).
\newblock AutoGen: Enabling next-gen LLM applications via multi-agent conversation.
\newblock \emph{arXiv:2308.08155}.

\bibitem{tran2025multiagent}
Tran, K.-T., Dao, D., Nguyen, M.-D., et~al. (2025).
\newblock Multi-agent collaboration mechanisms: A survey of LLMs.
\newblock \emph{arXiv:2501.06322}.

\bibitem{xi2023rise}
Xi, Z., Chen, W., Guo, X., et~al. (2023).
\newblock The rise and potential of large language model based agents: A survey.
\newblock \emph{arXiv:2309.07864}.

\bibitem{crewai2024}
CrewAI Inc. (2024).
\newblock CrewAI: Framework for orchestrating role-playing autonomous AI agents.
\newblock \url{https://github.com/crewAIInc/crewAI}.

\bibitem{langgraph2024}
LangChain Inc. (2024).
\newblock LangGraph: A framework for building stateful, multi-actor applications with LLMs.
\newblock \url{https://github.com/langchain-ai/langgraph}.

\bibitem{gong2024spatial}
Gong, Y. et~al. (2025).
\newblock Mitigating spatial hallucination in large language models for path planning via prompt engineering.
\newblock \emph{Scientific Reports}, 15:93601.

\bibitem{white2024prompt}
White, J., Hays, S., Fu, Q., Spencer-Smith, J., and Schmidt, D.~C. (2023).
\newblock A prompt pattern catalog to enhance prompt engineering with ChatGPT.
\newblock \emph{arXiv:2302.11382}.

\bibitem{kahneman1993when}
Kahneman, D., Fredrickson, B.~L., Schreiber, C.~A., and Redelmeier, D.~A. (1993).
\newblock When more pain is preferred to less: Adding a better end.
\newblock \emph{Psychological Science}, 4(6):401--405.

\bibitem{lewis2020retrieval}
Lewis, P., Perez, E., Piktus, A., et~al. (2020).
\newblock Retrieval-augmented generation for knowledge-intensive NLP tasks.
\newblock \emph{NeurIPS}, 33:9459--9474.

\bibitem{gao2024retrieval}
Gao, Y., Xiong, Y., Gao, X., et~al. (2024).
\newblock Retrieval-augmented generation for large language models: A survey.
\newblock \emph{arXiv:2312.10997}.

\bibitem{wang2023selfconsistency}
Wang, X., Wei, J., Schuurmans, D., et~al. (2023).
\newblock Self-consistency improves chain of thought reasoning in language models.
\newblock \emph{ICLR}.

\bibitem{qin2023toolllm}
Qin, Y., Liang, S., Ye, Y., et~al. (2023).
\newblock ToolLLM: Facilitating large language models to master 16000+ real-world APIs.
\newblock \emph{ICLR}.

\bibitem{travelbench2025}
Xie, T., Zhao, H., Hong, Y., et~al. (2025).
\newblock TravelBench: A real-world benchmark for multi-turn and tool-augmented travel planning.
\newblock \emph{arXiv:2512.22673}.

\bibitem{zhao2024poi}
Zhao, S., Zhao, T., Jin, H., Yang, F., and Li, Z. (2024).
\newblock A survey on point-of-interest recommendation: Models, architectures, and security.
\newblock \emph{arXiv:2410.02191}.

\bibitem{park2024prompt}
Park, J.~S., O'Brien, J.~C., Cai, C.~J., et~al. (2024).
\newblock The prompt report: A systematic survey of prompting techniques in natural language processing.
\newblock \emph{arXiv:2402.13066}.

\bibitem{zhang2023reasoning}
Zhang, Z., Zhang, A., Li, M., and Smola, A. (2023).
\newblock Large language models for reasoning: A survey.
\newblock \emph{arXiv:2412.15971}.

\bibitem{multiagentbench2025}
Talebirad, Y. and Nadiri, A. (2025).
\newblock MultiAgentBench: Evaluating the collaboration and competition of LLM-based agents.
\newblock \emph{ACL}.

\end{thebibliography}

\end{document}
